---
title: "Assignment_3"
author: "Vamshee Deepak Goud Katta"
date: "10/17/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# 1. Inserting Data and Libraries


## Reading the UniversalBank csv file and inserting approproate libraries

```{r}

library(class)
library(caret)
library(ISLR)
library(dummies)
library(dplyr)
library(tidyr)
library(ggplot2)

UBank_data <- read.csv("UniversalBank.csv")

```



# 2. Data Selection

```{r}

UBank_data_d <- dummy.data.frame(select(UBank_data, c(Personal.Loan, CreditCard, Online)))
head(UBank_data_d)

```



# 3. Data Partition


## Partitioning the UniversalBank dataset into Training and validation sets

```{r}

set.seed(123)
Index_Train <- createDataPartition(UBank_data_d$Personal.Loan, p=0.6, list = FALSE) 
# 60% of data is taken as Training Data

Train <- UBank_data_d[Index_Train,]
Validation <- UBank_data_d[-Index_Train,] 
# Rest of the data is taken as Validation Data

summary(Train)
summary(Validation)

```


# 4.  A. Creating Pivot table using Online, CC and Loan variables

```{r}

library(reshape2)
names(Train)
dcast(Train, Personal.Loan + CreditCard ~ Online)

```



# 5.  B. Naive Bayes Classification for customer with CC=1, Online=1, Personal.Loan=1
    
##         Total number of customers with CC=1 and Online=1 is 475+57 = 532
##         Number of customers with all variables as 1 is 57
##         Hence probability of customer taking personal loan is 57/532 = "0.1071"



# 6.  C. Preparing separate pivot tables for Loan against Online and Loan against CC


#     a) Loan v/s Online

```{r}

dcast(Train, Personal.Loan ~ Online)

```


#     b) Loan v/s CC

```{r}

dcast(Train, Personal.Loan ~ CreditCard)

```

# 7.   D. Computations of individual probabilities

##     i.    P(CC = 1 | Loan = 1) (the proportion of credit card holders among the loan acceptors)
##           Number of loan acceptors is 187+91 = 278
##           Number of Acceptors using credit cards is 91
##           Hence P(CC=1| Loan=1) = 91/278 = "0.3273"



##     ii.   P(Online = 1 | Loan = 1)
##           Number of loan acceptors is 99+179 = 278
##           Number of acceptors with online presence is 179
##           Hence P(Online = 1 | Loan = 1) = 179/278 = "0.6438"



##     iii.  P(Loan = 1) (the proportion of loan acceptors)
##           Total number of loan acceptors is 65+122+34+57 = 278
##           Hence proportion of loan acceptors = total of loan acceptors/total of customers = 278/3000 = "0.0926"



##     iv.   P(CC = 1 | Loan = 0)
##           Number of loan rejectors is 1930+792 = 2722
##           Number of rejectors with credit card is 792
##           Hence P(CC = 1 | Loan = 0) = 792/2722 = "0.2909"



##     v.    P(Online = 1 | Loan = 0)
##           Number of loan rejectors is 1102+1620 = 2722
##           Number of rejectors with online presence is 1620
##           Hence P(Online = 1 | Loan = 0) = 1620/2722 = "0.5951"



##     vi.   P(Loan = 0) (the proportion of loan rejectors)
##           Total number of loan rejectors is 785+1145+317+475 = 2722
##           Hence P(Loan = 0) = total of rejectors/total of customers = 2722/3000 = "0.9073"


```{r}
# 10. G. Modelling Naive Bayes on the Data set
library(e1071)

nb_model <-naiveBayes(Personal.Loan ~ CreditCard + Online , data = Train)
nb_model

```

#  8.   E.  Naive Bayes probability P(Loan = 1 | CC = 1, Online = 1)

##           = P(CC = 1 | Loan = 1) * P(Online = 1 | Loan = 1) * P(Loan = 1) / 
##           [P(CC = 1 | Loan = 1) * P(Online = 1 | Loan = 1) * P(Loan = 1)] + [P(CC = 1 | Loan = 0) * P(Online = 1 | Loan = 0) * P(Loan = 0)]

##           = 0.3273*0.6438*0.0926/(03273*0.6438*0.0926)+(0.2909*0.5951*0.9073)
##           = 0.0195/(0.0195+0.1570)

##           Hence P(Loan = 1 | CC = 1, Online = 1) = "0.1104"


#  9.   F.  The value obtained through Naive Bayes is slightly higher compared to the value of 0.1071, obtained from the pivot table which is more accurate compared to the Naive Bayes value


# 10.   G.  Using the model to find the entry corresponding to P(Loan = 1 | CC = 1, Online = 1)

```{r}

# Train
pred.class <- predict(nb_model, newdata = Train)

# validation
pred.prob <- predict(nb_model, newdata=Validation, type="raw") # probabilities
pred.class <- predict(nb_model, newdata = Validation) # class membership

# For the test set
df <- data.frame(actual = Validation$Personal.Loan, predicted = pred.class, pred.prob)

df[Validation$Personal.Loan == 1 & Validation$CreditCard == 1 & Validation$Online == 1,]

```

